% Place your vita below.

Qinkun Bao is a fifth-year Ph.D. student at the College of Information Sciences
and Technology, The Pennsylvania State University. He is a member of the Software 
System Security Research Lab, where he works under the supervision of Dr. Dinghao Wu.
His research interests span reverse engineering, binary analysis, and trusted computing. Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.


  \section*{Publications}
  \begin{enumerate}
    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}. (Technical Track)
    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}. (Artifact)
    
    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
    By Fuzzing and Memory Auditing'', under review.

    \item \textbf{Qinkun Bao}, Zihao Wang, Quan Li, and Dinghao Wu, ``Fast Semantic-aware Function Recognition in Obfuscated Binaries'', under review.
    
    \item Shixiong Jing, \textbf{Qinkun Bao}, Pei Wang, Xulong Tang, and Dinghao Wu, ``Characterizing AI Model Inference Applications Running in SGX Environment'', under review.
    
    \item Yufei Jiang, \textbf{Qinkun Bao}, Xiao Liu, and Dinghao Wu, ``RedDroid: Android Application Redundacy Customization based on Static Analysis'', in \emph{Proceedings of the 29th IEEE International Symposium on Software Reliability Engineering (ISSRE 2018)}, Memphis, TN, October 15-18, 2018
 
\item Pei Wang, \textbf{Qinkun Bao}, Li Wang, Shuai Wang, Zhaofeng Chen, Tao Wei, and Dinghao Wu, ``Software Protection On-The-Go: An Empirical Study on Mobile App Obfuscation'', in \emph{Proceedings of 40th International Conference on Software Engineering (ICSE 2018)}, Gothenburg, Sweden, May 27-June 3, 2018
  
\item Shengru Li, Kai Han, Nirwan Ansari, \textbf{Qinkun Bao}, Daoyun Hu, Junjie Liu, Shui Yu, and Zuqing Zhu, ``Improving SDN Scalability with Protocol-Oblivious Source Routing: A System-Level Study'', \emph{IEEE Transactions on Network and Service Management}, vol. 15, no. 1, pp. 275-288, March 2018
 
\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
\end{enumerate}





